Two subtle issues with over-representation analysis: Demonstration

### 2024-07-02 app/report.Rmd
no broom

suppressPackageStartupMessages({
  library("clusterProfiler")
  library("markdown")
  library("rmarkdown")
  library("shiny")
  library("broom")
  library("RhpcBLASctl")
  library("eulerr")
  library("plotly")
  library("DT")
  library("kableExtra")
})

>>>>

suppressPackageStartupMessages({
  library("clusterProfiler")
  library("markdown")
  library("rmarkdown")
  library("shiny")
  library("RhpcBLASctl")
  library("eulerr")
  library("plotly")
  library("DT")
  library("kableExtra")
})
